Automating Verification of MPC Security

### 2023-06-14 popl24/ygc.tex
checkpoint

  evaldecode(wv, p) { wv.k xor select(wv.p,v[1,OUTtt1],v[1,OUTtt2]) }

@@

%  andtable(keys, bt, ap, bp)
%  {
%    let r11 = (keys.k11 xor bt) in 
%    let r10 = (keys.k10 xor (not bt)) in
%    let r01 = (keys.k01 xor (not bt)) in
%    let r00 = (keys.k00 xor (not bt)) in
%    permute4(ap,bp,r11,r10,r01,r00)
%  }

>>>>

  evaldecode(wv) { wv.k xor select(wv.p,v[1,OUTtt1],v[1,OUTtt2]) }

@@

\begin{fpfig}[t]{Yao's Garbled Circuits, gate library type annotations.}{fig-ygc-types}
{\footnotesize
\begin{verbatimtab}
  garbledecode : string(gid)

  evaldecode   : { k = bool[1]; p = bool[1] }

  evalgate     : string(gid) *  { k = bool[1]; p = bool[1] } * { k = bool[1]; p = bool[1] }

  andgate      : string(gid) * string(ga) * string(gb)

  encode       : string(sa) * string(sb)
\end{verbatimtab}
}
\end{fpfig}
%  andtable(keys, bt, ap, bp)
%  {
%    let r11 = (keys.k11 xor bt) in 
%    let r10 = (keys.k10 xor (not bt)) in
%    let r01 = (keys.k01 xor (not bt)) in
%    let r00 = (keys.k00 xor (not bt)) in
%    permute4(ap,bp,r11,r10,r01,r00)
%  }
